Forecasting the black Sigatoka development rate: A comparison of machine learning techniques

### 2016-02-21 Paper Sigatoka - 2015.tex
2016-02-20

\usepackage{soul}
\usepackage{marginnote}

@@

\begin{figure}[h] 
 \centering
 \includegraphics[scale=.3]{Phase_one_Best_R2_for_each_algortihm}
 \caption{Phase one - Best $R^2$ for each algorithm} 
 \label{figura4} 
\end{figure}

@@

\begin{figure}[h] 
 \centering
 \includegraphics[scale=.3]{Phase_one_Best_R2_for_each_number_of_observation_range_in_the_patterm}
 \caption{Phase one - Best $R^2$ for each algorithm} 
 \label{figura5} 
\end{figure}

@@

\begin{figure}[h] 
 \centering
 \includegraphics[scale=.3]{Phase_one_Best_R2_for_variables}
 \caption{Phase one - Best $R^2$ for each variable combination} 
 \label{figura6} 
\end{figure}

\figurename $.$\ref{figura7} shows the pareto frontier with respect to $R^2$ and $RMSE$. Results are group by farm.

\begin{figure}[h] 
 \centering
 \includegraphics[scale=.6]{Phase_one_R2_RMSE}
 \caption{Phase one - Pareto frontier for $R^2$ and $RMSE$} 
 \label{figura7} 
\end{figure}

@@

>>>>

\usepackage{soul}
\usepackage{marginnote}
\usepackage{float}

@@

\begin{figure}[H] 
 \centering
 \includegraphics[scale=.5]{Phase_one_Best_R2_for_each_algortihm}
 \caption{Phase one - Best $R^2$ for each algorithm} 
 \label{figura4} 
\end{figure}

@@

\begin{figure}[H] 
 \centering
 \includegraphics[scale=.5]{Phase_one_Best_R2_for_each_number_of_observation_range_in_the_patterm}
 \caption{Phase one - Best $R^2$ for each algorithm} 
 \label{figura5} 
\end{figure}

@@

\begin{figure}[H] 
 \centering
 \includegraphics[scale=.5]{Phase_one_Best_R2_for_variables}
 \caption{Phase one - Best $R^2$ for each variable combination} 
 \label{figura6} 
\end{figure}

\figurename $.$\ref{figura7} shows the Pareto frontier for each farm with respect to $R^2$ and $RMSE$.

\begin{figure}[H] 
 \centering
 \includegraphics[scale=.8]{Phase_one_R2_RMSE}
 \caption{Phase one - Pareto frontier for $R^2$ and $RMSE$} 
 \label{figura7} 
\end{figure}

The Pareto frontier for the La Rita farm is composed by 96 elements. The \tablename $.$\ref{tabla2} shows the composition about variables and observation ranges.

\begin{table}[h] 
\caption{Composition of the Pareto frontier - La Rita - Phase one} 
\label{tabla2} 
\centering
\begin{tabular}{c|c|c|c|c} 
\hline
\bfseries Variable & \bfseries Observation range & \bfseries Quantity & \bfseries Max $R^2$ & \bfseries Min $RMSE$\\ 
\hline\hline 
Pair $\overline{T}_{a}$ $\overline{W}$ &	1 to 1  & 36 & 64.25\% & 714.51 \\
 &	2 to 1  & 6 & 62.97\% & 695.10 \\
\hline 
All  & 1 to 1  & 18 & 62.98\% & 701.95 \\
   & 2 to 1  & 12 & 61.76\% & 679.92 \\
    & 3 to 1  & 6 & 60.60\% & 676.42 \\
    & 5 to 1  &  2 & 60.37\% & 672.39 \\
\hline    
$\overline{T}_{a}$ & 1 to 1  & 12  & 63.60\% & 708.77 \\
       &	2 to 1  & 4 & 62.23\% & 689.55 \\
\hline
\end{tabular} 
\end{table}

Similarly, the Pareto frontier for the 28 Millas farm is composed by 75 elements. The \tablename $.$\ref{tabla3} shows the composition about variables and observation ranges.

\begin{table}[h] 
\caption{Composition of the Pareto frontier - 28 Millas - Phase one} 
\label{tabla3} 
\centering
\begin{tabular}{c|c|c|c|c} 
\hline
\bfseries Variable & \bfseries Observation range & \bfseries Quantity & \bfseries Max $R^2$ & \bfseries Min $RMSE$\\ 
\hline\hline 
Pair $\overline{T}_{a}$ $\overline{W}$ & 1 to 1 & 8 & 57.80\% & 438.09 \\
\hline 
All   &	9 to 1 & 2 & 50.93\% & 397.93 \\
  & 10 to 1	 & 2 & 50.97\% & 398.81 \\
  &	8 to 1 & 6 & 51.62\% & 398.93 \\
  &	7 to 1 & 2 & 52.25\% & 400.28 \\
  &	6 to 1 & 2 & 53.16\% & 404.14 \\
  &	4 to 1 & 2 & 54.32\% & 407.54 \\
\hline    
$\overline{T}_{a}$ & 1 to 1  & 8  & 59.09\% & 439.44 \\
\hline
Pair $\overline{T}_{a}$ $\overline{H}$ & 1 to 1	 & 8 & 57.51\% & 428.61 \\
 &	2 to 1 & 20 & 56.91\% & 414.37 \\
 &	3 to 1 & 3 & 54.41\% & 411.55 \\
 &	4 to 1 & 3 & 53.34\% & 406.65 \\
\hline
Pair $\overline{T}_{a}$ $P$ & 3 to 1 & 9 & 56.23\% & 422.76 \\
\hline
\end{tabular} 
\end{table}

@@

In the second phase, the best configurations obtained in phase one were used to validate with the last 50 and 100 weeks.

\figurename $.$\ref{figura8} shows the best $R^2$ for each algorithm in the experiment. Results are group by farm.

\begin{figure}[H] 
 \centering
 \includegraphics[scale=.5]{coming}
 \caption{Phase two - Best $R^2$ for each algorithm} 
 \label{figura8} 
\end{figure}

\figurename $.$\ref{figura9} presents, for one, two and three weeks ahead, the best $R^2$. Results are group by farm.

\begin{figure}[H] 
 \centering
 \includegraphics[scale=.5]{coming}
 \caption{Phase two - Best $R^2$ for each algorithm} 
 \label{figura9} 
\end{figure}

\figurename $.$\ref{figura10} shows the best $R^2$ for each variables combination. Results are group by farm.

\begin{figure}[H] 
 \centering
 \includegraphics[scale=.5]{coming}
 \caption{Phase two - Best $R^2$ for each variable combination} 
 \label{figura10} 
\end{figure}

\figurename $.$\ref{figura11} shows the Pareto frontier for each farm with respect to $R^2$ and $RMSE$.

\begin{figure}[H] 
 \centering
 \includegraphics[scale=.8]{coming}
 \caption{Phase two - Pareto frontier for $R^2$ and $RMSE$} 
 \label{figura11} 
\end{figure}
